Intersection of non-matching grids of different dimensions

### 2016-09-21 paper_intersections.tex
Add 13d prolongation description.

>>>>

\subsubsection{1D-3D prolongation}

\notePE{I suggest to denote IP, IPs intersection point and its plural respectively.}
% 1d-3d prolongation logic
% IP is:
% - 1D element node
%     - inside tetrahedron
%         - get the neighboring 1D element
%         - push to component queue candidate pair [1D neigbor -- tetrahedron]
%     - on the surface of tetrahedron
%         - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%         - get the tetrahedron neighbors on the faces
%         - push to bulk queue new candidates pairs:
%             - [current 1D element -- tetrahedron neighbor]
%             - [1D neighbor -- tetragedron neighbor]
%             - check whether the candidate pair has not been computed yet
%             (- if no new prolongation, push empty pair; means IP is on the boundary; 
%                the element is not closed then -- not fully covered with tetrahedrons)
% - inside 1D element
%     - get all faces in which the IP lies (1 face, or 2 faces (edge), or 3 faces (node))
%     - get the tetrahedron neighbors on the faces
%     - push to bulk queue candidate pair [current 1D element -- tetrahedron neighbor]
%     - check whether the candidate pair has not been computed yet
%     (- if no new prolongation, push empty pair; same meaning as above)

A new candidate pair of elements is found during prologantion, based on the topological information of the intersection point. There are 3 possible cases:

\begin{itemize}
    \item \textbf{IP lies at 1D element node and inside 3D element} \\
            We find the neighboring 1D element over the node and push a new candidate pair [1D neighbor -- current 3D element] into component queue.
    \item \textbf{IP lies at 1D element node and on the surface of 3D element} \\
            We find all the faces of 3D element in which the IP lies (1 face, or 2 faces (IP on an edge), 
            or 3 faces (IP at a node)). We find the corresponding neghboring 3D elements over the faces and
            push the following new candidates pairs into the bulk queue: [current 1D element -- 3D neighbor], [1D neighbor -- 3D neighbor].
            If the candidates pair has been investigated already, we skip it.
    \item \textbf{IP lies inside 1D element node (therefore must be on the surface of 3D element)} \\
            The same as before, but we push only [current 1D element -- 3D neighbor] candidates pairs, since
            there is no 1D neighbor.
\end{itemize}
